












\documentclass{resume} 

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Manoj V} 
\address{Nemili, Ranipet- 631051 \\ +91 7358878062 \\ manoj.venu@outlook.com}
\address{linkedin.com/manojvenu \\ github.com/ManoMedEngg} 
\address{\bf Biomedical Engineer }




\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
%\linkedin{vedhavalli}
%\github {vedhavalli2513}

\begin{rSection}{Career Objective}
I’m a Biomedical Engineering graduate with real-world training in handling and checking hospital equipment. I’m looking for a Field Service and Quality Checking Engineer role where I can use my skills to make sure medical devices work safely and properly. I’m eager to learn more, grow in this field, and help improve patient care through quality service.
    
\end{rSection}



\begin{rSection}{Education}


{\bf Kings Engineering College, Sriperumbudur} \hfill{August 2022 -Present} \\{B.E. Biomedical Engineering} \hfill{CGPA: 7.4} \\{\bf Government Boys Higher Secondery School, Nemili} \hfill {June 2021 - May 2022} \\{HSC}\hfill {Percentage: 57 }\\{\bf Vivekanandha Metric Higher Secondary School, Nemili} \hfill {June 2019 - May 2020} \\{SSLC}\hfill {Percentage: 87 }


\begin{rSection}{Professional Experience}
\begin{itemize}
\item {\bf Chennai Natinol Hospital- Chennai(Trainee)}\hfill{Aug-Now 2025}\\

\item {\bf KV's Biomedical- Chennai(Trainee)}\hfill{July 2025}\\
Advanced training in industrial biomedical systems.
\item {\bf Peacock Hospitals Pvt Ltd- Thiruthani(Intern)}\hfill{May-Jun 2025}\\
 Actively Perform in Daily Checking on ER department and OT department.
\item{\bf Dr. Venkateshwara Ortho and Trauma Care- Kanchipuram(Intern)}\hfill{ May 2025}\\
  Assist for an OT Biomedical Engineering to implant a Petella.
  \item{\bf Sri Ne Medical Foundation- Kanchipuram(Intern)}\hfill{ Jan-Feb 2025}\\
  Assist for radiological equipments calibrating and quality assurance (QA).
\end{itemize}
\end{rSection}

\begin{rSection}{Skills}
%\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }

{\bf Tool based Hard Skills} \begin{itemize}
    \item VS code - Source code editing 
     \item Ki Cad, Eagle cad - PCB designing
     \item Google Workspace - Docs, Sheets, Drive, Gmail, etc. 
    \item MS Office - Word, Excel, PowerPoint
    \item Overleaf - Documentation
    \item Matlab - Signal Processing and Image Processing
\end{itemize} 
\vspace{0.5cm}
{\bf Hard Skills:} Embedded System, Linux, File Management, HTML, CSS, Clinical laboratory\\

{\bf Soft Skills:}  Leadership, Team building, Problem Resolution
%\end{tabular}

\end{rSection}
\end{rSection}


\newpage

\begin{rSection}{Events/Courses}
\smallskip
{\bf Smart India Hackathon}
\begin{itemize}
\item IoMT- Smart device for legacy medical device. \hfill 2025\\
Selected as top 3 best idea over 150+ teams in Internal Hachathon.
\item Cost Effective Myoelectric Prosthetic Hand. \hfill 2024\\
Selected as best idea from the department.
\end{itemize}

\smallskip
{\bf Paper Presentation}
\begin{itemize}
\item IoT Based IV Bag Monitoring System.
\item Patient Monitoring System in Tele Medicine.
\item Automated Pharmacy.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------------------------
%\smallskip
%{\bf Spoken Tutorial}
%\begin{itemize}
 %   \item 2023- Arduino, Biopython.
  % \item  2024- HTML(Web Development), Cell Designer, Open PLC with LD Micro. 
%\end{itemize}
%\smallskip


%\smallskip
%{\bf Naan Mudhalvan}
%\begin{itemize}
%\item 2023- Microsoft Essentials
%\item 2024- Experience Based Project Learning(IoT)
%\item 2025- 4G,5G Communication and Network
%\end{itemize}
    
%\end{rSection}

%----------------------------------------------------------------------------------------------------------


\begin{rSection}{Conference}

\begin{itemize}
    \item[1.] \textbf{International Conference on Recent Trends and Development in Electrical and Power Engineering by Bharat Institute of Higher Education and research [ICRTDEPE 2024]}\\
    In this conference I submit a paper a Navigating Surgical Emergencies: The impact of power outages.
    \item[2.] \textbf{International Conference on Innovation and Technology by Kings Engineering College [ICICET 2024]}\\
    In this conference I submit a paper about a IoT Based IV bag Monitoring and Switching System.
\end{itemize}
\end{rSection}


\begin{rSection}{Research Work}
{\bf IoT Based Stethoscope (2023 - In Progress)}\\
%An IoT-based stethoscope enhancing digital technology to amplify and  transmit heart and lung sounds wirelessly for remote monitoring. This innovation enhances telemedicine by allowing healthcare professionals to make accurate diagnoses without being physically present. It is particularly valuable in emergencies and for patients in remote locations, improving accessibility and patient care.

\end{rSection}

\begin{rSection}{Declaration}
    I hereby declare that the information provided above is true to the best of my knowledge and belief.
\end{rSection}



\vspace{2cm}

\noindent\textbf{Date:}\\ 

\textbf{Place:} Chennai \hfill{\bf Manoj V}

%-----------------------------------------------------------------------------------------------%-------------------------------------------------------
%\personalinfo{%

 % \email{manoj.venu@outlook.com}\\
  %\phone{+91 7358878062}\\
  %\%mailaddress{Nemili, Ranipet-631051}\\
  %\linkedin{linkedin.com/manojvenu}\\
  %\github{github.com/ManoMedEngg}

%\begin{fullwidth}
%\makecvheader
%\end{fullwidth}

\end{document}
%--------------------------------------------------------------------------
%------------------------------------------------------------------------------